---
title: "Stimulus Data"
author: "Abhraneel Sarma"
date: "7/26/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(modelr)
library(tidybayes)
```


## Stimuli

We are using the following stimuli to test:

- scatterplot / raw data
- mean point estimate
- mean point estimate with 95% confidence intervals
- gradient plot
- hypothetical outcome plots
- quantile dot plots
- cumulative distribution function
- cumulative distribution function + probability density function
- ensemble plots (overlay of low opacity bootstrapped means)


## Data generation
There are two approaches that we can use for generating the data.
The first is a more controlled approach where we manipulate the effect sizes by choosing different values of mean and standard deviation. This allows us to test for a range of pre-determined effect sizes.

The second is a more natural approach, where we assume the data is being generated from a hierarchical model where the means for each region and each product are modelled as random effects i.e. arise from two different zero centered normal distributions.

```{r, data-gen-env}
ntrials = 10
nstores = 100
nstore_samples = 10
nregions = ntrials
effect_sizes = c(1/5, 1/4, 1/3, 1/2, 4/5)
means = c(9, 11, 12)
```

### Data generation using fixed effect sizes

```{r, data-gen-1}
set.seed(127128746)
baseline = 10

data.sim = crossing( 
  trial = seq(1:ntrials),
  baseline = baseline,
  effect_size = effect_sizes,
  mean = means
) %>%
  mutate( sd = ifelse(abs(baseline - mean) > 0, abs(baseline - mean) / effect_size, 0 ) ) %>%
  filter( sd != 0 ) %>%
  arrange( mean, effect_size ) %>%
  mutate(
    idx = seq(1:nrow(.)),
    region = map_chr(idx, function(.x) {
      set.seed((.x))
      paste0(sample(LETTERS, 4), collapse = "")
    }),
    profit = map2( mean, sd, ~ rnorm(nstores, .x, .y) )
  )
```


```{r}
data.sim.samples = data.sim %>%
  mutate( samples = map(profit, ~sample(.x, nstore_samples))) %>%
  select(-profit)

data.sim.samples %>%
  filter( effect_size == 1/5 ) 
```

```{r, plot-data1-raw, fig.height = 12, fig.width = 16}
data.sim.samples %>%
  filter( effect_size == 4/5 ) %>%
  mutate( store_idx = list(rep(1:nstore_samples)) ) %>%
  unnest( c(samples, store_idx) ) %>%
  ggplot(aes(x = store_idx, y = samples)) +
  geom_col() +
  scale_x_continuous( breaks = seq(0, 10, by = 2) ) +
  geom_hline( yintercept = baseline, color = "red", alpha = 0.5 ) +
  coord_cartesian( ylim = c(0, 18)) +
  ggtitle( "Mean profit (over the past 25 weeks) for a product in 4 different regions" ) +
  facet_wrap( ~ region , ncol = 6 )
```


```{r, warning = FALSE, plot-data1-mean_qi, fig.height = 12, fig.width = 16}
data.sim.samples %>%
  filter( effect_size == 4/5 ) %>%
  unnest( c(samples) ) %>%
  group_by(region) %>%
  mean_qi(samples, .width = c(.95)) %>%
  ggplot(aes(x = NA, y = samples) ) +
  geom_pointinterval() +
  geom_hline( yintercept = baseline, color = "red", alpha = 0.5 ) +
  coord_cartesian( ylim = c(0, 18)) +
  facet_wrap( ~ region , ncol = 6 ) +
  theme( axis.ticks.x = element_blank(), axis.text.x = element_blank() )
```


### Data generation using a hierarchical model

$$
sales_{i, j} \sim \mathrm{Normal( \mu_{i, j}, \sigma)} \\
u_{i, j} = \alpha_0 + \alpha_{product[i]} + \alpha_{region[j]} \\
\alpha_0 \sim \mathrm{Normal(3, 1)} \\
\alpha_{product[i]} \sim \mathrm{Normal(0, \sigma_p)} \\
\alpha_{region[j]} \sim \mathrm{Normal(0, \sigma_r)}
$$


We then sample using this data generation process to get the simulated data set.

```{r, data-generation}
set.seed(74124)
mu_region = rep(rnorm(nregions * ntrials, 0, sd), each = nproducts)
mu_product = rep(rnorm(nproducts * ntrials, 0, 1), nregions)

data.sim <- crossing(
    trial = seq(1:ntrials),
    region.idx = seq(1:nregions),
    product = factor( LETTERS[1:nproducts] ),
    a_bar = 5,
    sd = sd,
    sigma = sd * 10,
  ) %>%
  mutate( 
    region = map2_chr(trial, region.idx, function(.x, .y) {
      set.seed((.x*10 + .y))
      paste0(sample(LETTERS, 3), collapse = "")
    }) 
  ) %>%
  mutate(
    mu_region = mu_region,
    mu_product = mu_product,
    true_mu = rnorm(N, a_bar, sd) + mu_product + mu_region,
    sd = sigma / sqrt(Ni),
    profit = map2( true_mu, sigma, ~rnorm(Ni, .x, .y))
  )
```


### 1. Raw data

```{r plot-data2-raw}
data.sim %>%
  filter( trial == 1) %>%
  mutate( .value = map_dbl(profit, ~mean(.x)) ) %>%
  ggplot(aes(x = product, y = .value)) +
  geom_col() +
  facet_wrap( ~ region, nrow = 2 ) +
  coord_cartesian( ylim = c(0, 8)) +
  ggtitle( "Mean profit (over the past 25 weeks) for a product in 4 different regions" )
```


```{r, gen-data-raw}
for(i in 1:ntrials) {
    p <- data.sim %>%
        filter( trial == i) %>%
        mutate( .value = map_dbl(profit, mean)) %>%
        ggplot(aes(x = product, y = .value)) +
        geom_col() +
        facet_wrap( ~ region, nrow = 2 ) +
        coord_cartesian( ylim = c(0, 8)) +
        ggtitle( "Mean profit (over the past 25 weeks) for a product in 4 different regions" )
    
    ggsave(filename = paste0('../plots/raw-data/profits-', i, '.png'), height = 6, width = 9, units = "in", dpi = 150, plot = p, device = "png")
}
```

### 1. Raw data

```{r, plot-data-raw}
data.sim %>%
  sample_n(4) %>%
  unnest(profit) %>%
  ggplot(aes(x = product, y = profit)) +
  geom_point( alpha = 0.5, position = position_jitter(width = 0.1) ) +
  facet_wrap( ~ region, ncol = 4 ) +
  geom_hline( yintercept = target, color = "red", alpha = 0.5 ) +
  coord_cartesian( ylim = c(0, 15)) +
  ggtitle( "Profits (for the past 25 weeks) from a sample of 25 stores in 4 different regions" )
```


### 2. Mean

```{r, plot-data-raw}
data.sim %>%
  sample_n(4) %>%
  mutate( .value = map_dbl(profit, mean)) %>%
  ggplot(aes(x = product, y = .value)) +
  geom_col() +
  facet_wrap( ~ region, ncol = 4 ) +
  geom_hline( yintercept = target, color = "red", alpha = 0.5 ) +
  coord_cartesian( ylim = c(0, 8)) +
  ggtitle( "Mean profit (for the past 25 weeks) from a sample of 25 stores in 4 different regions" )
```


```{r, bootstrap_mean}
bootstrap_mean <- function(x, n = 5000) {
  if (is_list(x)) x = flatten_dbl(x)
  iter = 1:n
  map_dbl(iter, function(.x){
    set.seed(.x)
    mean(sample(x, length(x), replace = TRUE))
  }) 
}

data.sim.boot = data.sim %>%
  mutate( boot.mean = map(profit, bootstrap_mean))
```

### 3. Ensemble sample of means

```{r, plot-mean-ensemble, fig.width = 12, fig.height = 5}
data.sim.boot %>%
  filter(trial == 1) %>%
  mutate( .value = map(boot.mean, ~sample(.x, 50))) %>%
  unnest( .value ) %>%
  ggplot(aes(x = NA, y = .value)) +
  geom_point( position = position_jitter(width = 0.2), alpha = 0.5 ) +
  coord_cartesian( ylim = c(0, 10) ) +
  geom_hline( yintercept = 5, alpha = 0.5, color = "red" ) +
  facet_grid( . ~ region ) +
  ggtitle( "Mean profit (over the past 50 weeks) for a product in 4 different regions" )
```

```{r, plot-mean-ensemble}
data.sim.boot %>%
  sample_n(4)  %>%
  mutate( .value = map(boot.mean, ~sample(.x, 50))) %>%
  unnest( .value ) %>%
  ggplot(aes(x = NA, y = .value)) +
  geom_point( position = position_jitter(width = 0.2), alpha = 0.5 ) +
  coord_cartesian( ylim = c(0, 10) ) +
  geom_hline( yintercept = 5, alpha = 0.5, color = "red" ) +
  facet_grid( . ~ region ) +
  ggtitle( "Bootstrap mean profit (for the past 25 weeks) from a sample of 25 stores in 4 different regions" )
```

### 4. Mean + 95% confidence intervals

```{r, gen-mean-ci, fig.width = 12, fig.height = 5}
for(i in 1:ntrials) {
    p <- data.sim.boot %>%
        filter(trial == i) %>%
        unnest( boot.mean ) %>%
        group_by(region) %>%
        mean_qi(boot.mean, .width = .95) %>%
        ggplot(aes(y = boot.mean, x = NA)) +
        geom_pointinterval() +
        coord_cartesian( ylim = c(0, 10)) +
        facet_wrap( ~ region, ncol = 4 ) +
        geom_hline( yintercept = 5, alpha = 0.5, color = "red" ) +
        ggtitle( "Bootstrap mean profit (for the past 25 weeks) from a sample of 25 stores in 4 different regions" )
    
    ggsave(filename = paste0('../plots/mean-ci/profits-', i, '.png'), height = 4.5, width = 8, units = "in", dpi = 150, plot = p, device = "png")
}
```

```{r, plot-mean-ci, fig.width = 12, fig.height = 5}
data.sim.boot %>%
  sample_n(4) %>%
  unnest( boot.mean ) %>%
  group_by(region) %>%
  mean_qi(boot.mean, .width = .95) %>%
  ggplot(aes(y = boot.mean, x = NA)) +
  geom_pointinterval() +
  coord_cartesian( ylim = c(0, 10)) +
  facet_wrap( ~ region, ncol = 4 ) +
  geom_hline( yintercept = 5, alpha = 0.5, color = "red" ) +
  ggtitle( "Bootstrap mean profit (for the past 25 weeks) from a sample of 25 stores in 4 different regions" )
```


### 5. Gradient plots

```{r, fig.width = 7, fig.height = 3}
data.sim.boot %>%
  sample_n(4) %>%
  unnest( boot.mean ) %>%
  group_by(region) %>%
  ggplot(aes(y = boot.mean, x = NA)) +
  stat_gradientinterval(fill = "blue", show_interval = TRUE) +
  scale_alpha_continuous(range = c(0, 1)) +
  coord_cartesian( ylim = c(0, 10)) +
  facet_wrap( ~ region, ncol = 4 ) +
  labs( alpha = "density" ) +
  geom_hline( yintercept = 5, alpha = 0.5, color = "red" ) +
  ggtitle( "Mean profit (over the past 50 weeks) for products in 4 regions" )
```

### 6. PDF

```{r, plot-mean-density}
data.sim %>%
  sample_n(4) %>%
  ggplot( aes(x = NA, dist = "norm", arg1 = true_mu, arg2 = sd) ) +
  stat_dist_halfeye() +
  coord_cartesian( ylim = c(0, 10)) +
  facet_wrap( ~ region, ncol = 4 ) +
  geom_hline( yintercept = 5, alpha = 0.5, color = "red" ) +
  ggtitle( "Mean profit (over the past 50 weeks) for products in 4 regions" )
```

### 7. Hypothetical outcome plots

```{r, hops, fig.width = 12, fig.height = 3}
n_samples = 20

data.sim.boot %>%
  sample_n(4) %>%
  unnest( boot.mean ) %>%
  group_by(region) %>%
  sample_n( n_samples ) %>%
  mutate( mean.index = 1:n_samples) %>%
  ggplot(aes(x = NA, y = boot.mean)) +
  geom_col() +
  facet_wrap( ~ region )  +
  geom_hline( yintercept = 5, alpha = 0.5, color = "red" ) +
  ggtitle( "Mean profit (over the past 50 weeks) for products in 4 regions" ) +
  gganimate::transition_manual( mean.index )
```

### 8. Quantile dotplot


```{r, quantile_dotplot}
library(forcats)

data.sim.boot %>%
  sample_n(4) %>%
  unnest( boot.mean ) %>%
  mutate( region = as.factor(region)) %>%
  group_by(region) %>%
  do(tibble(mean = quantile(.$boot.mean, ppoints(20)))) %>%
  ggplot(aes(x = mean)) +
  geom_dotplot(binwidth = 0.5) +
  scale_y_continuous(breaks = NULL) +
  ggtitle( "Mean profit (over the past 50 weeks) for products in 4 regions" ) +
  facet_grid( . ~ region)
```

### 9. Cumulative distribution function

```{r, cdf, fig.width = 12, fig.height = 6}
n_samples.cdf = 100

endpoints = d %>%
  select(index, diff, region) %>%
  mutate(mean = 4, cdf = 1)

d %>%
  unnest(boot.mean)  %>%
  group_by(index, diff, region) %>%
  do(tibble(mean = quantile(.$boot.mean, ppoints(n_samples.cdf)))) %>%
  mutate( cdf = (1:n_samples.cdf)/n_samples.cdf ) %>%
  ungroup() %>%
  rbind(endpoints) %>%
  filter( diff == -0.125) %>%
  ggplot(aes(x = mean, y = cdf)) +
  geom_area() +
  facet_grid( region ~ index ) +
  coord_cartesian(xlim = c(1.5, 2.5), ylim = c(0, 1.2)) +
  scale_y_continuous( breaks = seq(0, 1.5, by = 0.5) )
```


------------------ Ignore ------------------
## Scenario 2: Correlation

Multivariate gaussian https://stat.ethz.ch/R-manual/R-devel/library/MASS/html/mvrnorm.html
1. positive correlation 
2. negative correlation
3. no correlation

```{r, message = FALSE}
variance <- 4
sigmas <- list(
    matrix(c(1, 0, 0, 1), 2, 2),
    matrix(c(1, 0.3, 0.3, 1), 2, 2),
    matrix(c(1, -0.3, -0.3, 1), 2, 2)
  )

set.seed(100)
mvt_df = crossing(
  size = c(50, 100, 200),
  sigma = sigmas
) %>%
  mutate(
    mean = list(c(3, 1)),
    j = seq(1:nrow(.)),
    sigma = map(sigma, ~ .x * variance),
    mvt_data = pmap(list(size, mean, sigma), ~MASS::mvrnorm(..1, ..2, ..3) %>%
                  as_tibble(.name_repair = "unique") %>%
                  rename( "x" = '...1', "y" = "...2" ) %>%
                  mutate( index = seq(1:nrow(.))))
  )
```

### Set of possible insights

1. There is no correlation between x and y (TRUE for 1, 4, 7)
2. There is a small positive correlation between x and y (TRUE for 2, 5, 8 )
3. There is a small negative correlation between x and y  (TRUE for 3, 6, 9 )


### Baseline

```{r, message = FALSE, fig.width = 12, fig.height = 4}
n = 100

mvt_df.disaggregated = mvt_df %>%
  unnest(mvt_data) %>%
  select(index, everything()) 

mvt_df.disaggregated %>%
  filter(size == n) %>%
  ggplot() + 
  geom_point(aes(x, y)) +
  facet_wrap( ~ j ) +
  coord_cartesian( xlim = c(-5, 10), ylim = c(-3, 7))
```

```{r, results = "hide", message = FALSE}
mvt_df = mvt_df %>%
  mutate(fit = map(mvt_data, ~ stan_glm(y ~ x, data = .x)))
```


### 2. Mean regression line

```{r}
#newdata = data.frame(x = seq(0, 8, by = 0.2))
mvt.draws = mvt_df %>%
  mutate(
    # newdata = map(mvt_data, ~ data_grid(., x = seq_range(.$x, n = 21))),
    newdata = list(tibble(x = seq(-5, 9, by = 0.2))),
    means = map2(newdata, fit, ~ add_fitted_draws(.x, .y))
  )
```


```{r, fig.width = 12, fig.height = 4}
mvt.draws  %>%
  filter( size == n ) %>%
  unnest(means, .preserve = c(size, sigma, mean, mvt_data)) %>%
  ggplot() +
  stat_lineribbon(aes(x = x, y = .value), .width = 0) +
  scale_fill_brewer() +
  coord_cartesian( xlim = c(-5, 10), ylim = c(-4, 7)) +
  facet_wrap( ~ j )
```

```{r, fig.width = 12, fig.height = 4}
mvt.draws  %>%
  filter( size == n ) %>%
  unnest(means, .preserve = c(size, sigma, mean, mvt_data)) %>%
  ggplot() +
  stat_lineribbon(aes(x = x, y = .value), .width = 0) +
  geom_point(data = filter(mvt_df.disaggregated, size == n), aes(x, y), alpha = 0.4) +
  scale_fill_brewer() +
  coord_cartesian( xlim = c(-5, 10), ylim = c(-4, 7)) +
  facet_wrap( ~ j )
```


```{r, fig.width = 12, fig.height = 4}
mvt.draws  %>%
  filter( size == 50 ) %>%
  unnest(means, .preserve = c(size, sigma, mean, mvt_data)) %>%
  ggplot() +
  stat_lineribbon(aes(x = x, y = .value)) +
  scale_fill_brewer() +
  coord_cartesian( xlim = c(-5, 10), ylim = c(-4, 7)) +
  facet_wrap( ~ j )
```


```{r, fig.width = 12, fig.height = 4}
mvt_ensembles = mvt_df %>%
  filter( size == 50 ) %>%
  mutate(
    # newdata = map(mvt_data, ~ data_grid(., x = seq_range(.$x, n = 21))),
    newdata = list(tibble(x = seq(-5, 9, by = 0.2))),
    means = map2(newdata, fit, ~ add_fitted_draws(.x, .y, n = 100))
  ) %>%
  unnest(means, .preserve = c(size, sigma, mean, mvt_data))

mvt_ensembles %>%
  ggplot() +
  geom_line(aes(x = x, y = .value, group = .draw), alpha = 0.1, color = "#08519C") +
  #geom_point() +
  coord_cartesian( xlim = c(-5, 10), ylim = c(-4, 7)) +
  facet_wrap( ~ j)
```

```{r, fig.width = 12, fig.height = 4}
p <- mvt_ensembles %>%
  filter(j == 1) %>%  
  ggplot() +
  geom_line(aes(x = x, y = .value, group = .draw), color = "#08519C") +
  coord_cartesian( xlim = c(-5, 10), ylim = c(-4, 7)) +
  #geom_point() +
  gganimate::transition_manual( .draw )

gganimate::animate(p, fps = 3)
```

