---
title: 'Stimuli data generation #2'
author: "Abhraneel Sarma"
date: "10/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(modelr)
library(tidybayes)
library(gamlss.dist)

theme_set( theme_light() ) +
  theme_update(
    panel.border = element_blank(),
    panel.grid.major = element_line(colour = "#666666", size = 0.1),
    panel.grid.minor = element_line(colour = "#666666", size = 0.1),
    panel.background = element_rect(fill = "transparent",colour = NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_text( size = 24 ),
    axis.title.y = element_text( size = 27 )
  )
```

## Study design
We manipulate the probability of the alternate hypothesis being true $P(H_1 = True) = 1 - p_{null}$, at consistent intervals between (0.5 and 1). We incentivise participants based on this probability.

- if $P(H_1 = True) = 0.5$, $Payoff_{TP} = Payoff_{FP} = Payoff_{TN} = Payoff_{FN}$
- if $P(H_1 = True) = 0.9$, $Payoff_{FP} = - 9 \times Payoff_{TP}$, $Payoff_{FN} = -1/9 \times Payoff_{TN}$ (_Note: we need to figure out the relationship between $Payoff_{TP}$ and $Payoff_{FN}$_)

For each value of $p_{null}$, we show participants k graphs with 10 data points in each graph. These graphs show the profits of 10 randomly sampled stores from a region with n stores. We ask them if, based on this sample, the stores are meeting a designated profit margin.

## Stimuli
We are using the following stimuli to test:

- scatterplot / bar chart / raw data (with mean point estimate?)
- mean point estimate with 95% confidence intervals
- gradient plot
- hypothetical outcome plots
- quantile dot plots
- cumulative distribution function
- cumulative distribution function + probability density function
- ensemble plots (overlay of low opacity bootstrapped means)


## Data generation

- different mean and sd combinations such that the effect size is consistent
- different effect sizes (so that we can control for effect size)

```{r setup_vars}
# we will load the data instead
set.seed(7841)
sample_size = 20
n_trials = 10
n_stores = 200
n_regions = 10
baseline = 0
p_h1_levels = 0.5 # c(seq(2, 8))
effect_sizes = c(0.2, 0.3, 0.5)
means = 1
```


```{r eval = FALSE}
data.sim <- crossing( 
    trial = seq(1:n_trials),
    baseline = baseline,
    p_h1 = p_h1_levels,
    mu = means,
    effect_size = effect_sizes
  ) %>%
  mutate(
    sd = mu / effect_size,
    mu = map2(p_h1, mu, ~ (rbinom(n_regions, 1, .x) * .y)), #map2( mu, p_h1, ~ c(rep(.x, .y), rep(0, n_regions - .y)) ),
    # mu = map(mu, ~ sample(.x, size = n_regions) ),
    # p_h1 = p_h1 / 10,
    trial = 1:nrow(.)
  ) %>%
  unnest( cols = c(mu) ) %>%
  mutate( 
    region_idx = rep(1:n_regions, n_trials * length(means) * length(effect_sizes)),
    data = map2(mu, sd, ~ rnorm(n_stores, .x, .y))
  )

data.sample <- data.sim %>%
  mutate(
    profit = map(data, ~sample(., sample_size)),
    idx = seq(1:nrow(.)),
    region = map_chr(idx, function(.x) {
      set.seed((.x))
      paste0(sample(LETTERS, 4), collapse = "")
    }),
    store_idx = list(rep(1:sample_size))
  )

#save(data.sample, data.sim, file = "../data/simulated_data.RData")
```

```{r, sample}
load("../data/simulated_data.RData")

nu = sample_size - 1
```

```{r, bootstrap_mean}
bootstrap_mean <- function(x, n = 5000) {
  if (is_list(x)) x = flatten_dbl(x)
  iter = 1:n
  map_dbl(iter, function(.x){
    set.seed(.x)
    mean(sample(x, length(x), replace = TRUE))
  }) 
}

data.sim.boot = data.sample %>%
  dplyr::select( -data ) %>%
  mutate( boot.mean = map(profit, bootstrap_mean))
```


```{r}
limits = data.sim.boot %>%
  unnest( cols = c(boot.mean)) %>%
  summarise(min = floor(min(boot.mean)), max = ceiling(max(boot.mean))) %>%
  gather() %>%
  magrittr::extract2("value")
```


```{r}
data.sample %>%
  mutate(
    estimate = round(map_dbl(data, ~t.test(.x, conf.level = 0.9)$p.value), digits = 5),
    estimate_10pc = estimate < 0.1,
    estimate_5pc = estimate < 0.05,
    estimate_1pc = estimate < 0.01
  ) %>%
  dplyr::select(-c(baseline, p_h1, effect_size, data, profit, idx, region, store_idx)) %>%
  write.csv(file = "../data/true_effects.csv")
```

## Visualizations

### 1.1. Scatterplot of raw data with jitter

```{r, scatterplot, fig.width = 10, fig.height = 4, warning = FALSE}
data.sample %>%
  unnest( cols = c(profit, store_idx) ) %>%
  filter( trial == 2, region_idx == 3 ) %>%
  ggplot(aes(x = NA, y = profit)) + 
  geom_jitter( width = 0.2, alpha = 0.7) + 
  facet_wrap( ~ region, ncol = 5 ) +
  geom_hline( yintercept = 0, color = "red", alpha = 0.5 ) +
  ylim(limits)
```


Below, we generate these plots and save it as images to be used in the pilot study.

```{r, scatterplot_save, fig.width = 3, fig.height = 4, eval = FALSE}
for(i in 1:n_regions) {
  for(j in 1:(n_trials * length(effect_sizes) * length(means))) {
    p <- data.sample %>%  
        unnest( cols = c(profit, store_idx) ) %>%
        filter( trial == j & region_idx == i ) %>%
        ggplot(aes(x = NA, y = profit)) + 
        geom_jitter( width = 0.2, alpha = 0.7) +
        geom_hline( yintercept = 0, color = "red", alpha = 0.5 ) +
        ylim(c(-15, 15))
      
      ggsave(filename = paste0('../plots/raw-data/profits-t', j,'-p0.5-', i, '.png'), height = 8, width = 5, units = "in", dpi = 72, plot = p, device = "jpeg") 
  }
}
```

### 2. Mean point estimate with error bars showing the 95% intervals for the data
This is not used

```{r, mean_ci, fig.width = 10, fig.height = 4, warning = FALSE}
data.sample %>%
  mean_qi(profit, .width = c(.95)) %>%
  select( - store_idx ) %>%
  filter( trial == 2  ) %>%
  ggplot(aes(x = NA, y = profit)) + 
  geom_pointinterval() +
  geom_point(aes(x = NA, y = profit), size = 4) +
  facet_wrap( ~ region, ncol = 5 ) +
  geom_hline( yintercept = 0, color = "red", alpha = 0.5 )
```

### 3. Bootstrapped ensembles

```{r, fig.width = 10, fig.height = 4}
data.sim.boot %>%
  filter(trial == 1) %>%
  mutate( .value = map(boot.mean, ~sample(.x, 50))) %>%
  unnest( .value ) %>%
  ggplot(aes(x = NA, y = .value)) +
  geom_point( position = position_jitter(width = 0.2), alpha = 0.5 ) +
  geom_hline( yintercept = 0, alpha = 0.5, color = "red" ) +
  facet_wrap( . ~ region, ncol = 5 )
  #ggtitle( "Mean profit for a product in 10 different regions" )
```

### 4. Bootstrapped means with 95% CI

```{r}
data.sample %>%
  filter( trial == 3 & region_idx == 1 ) %>%
  rename( sample = profit, population = data) %>%
  mutate( 
    pop_mean = map_dbl(population, mean),
    mean = map_dbl(sample, mean),
    se = map_dbl(sample, ~sd(.x)/sqrt(length(.x))),
    .lower = qTF(0.025, mean, se, nu = nu),
    .upper = qTF(0.975, mean, se, nu = nu)
  ) %>%
  ggplot() + 
  geom_pointinterval(aes(x = 0.5, y = mean), fill = "#333333", point_size = 5, interval_size = 12) +
  geom_point(aes(x = -0.5, y = pop_mean), color = "#C44232", size = 5) +
  geom_hline( yintercept = 0, color = "red", alpha = 0.5 ) +
  scale_y_continuous( limits = limits, breaks = seq(limits[[1]], limits[[2]], by = 2) ) +
  xlim(-3, 3)
```


```{r, fig.width = 10, fig.height = 4, eval = FALSE}
for(i in 1:n_regions) {
  p <- data.sample %>%
    filter(trial == 3 & region_idx == i) %>%
    rename(sample = profit, population = data) %>%
    mutate( 
      pop_mean = map_dbl(population, mean),
      mean = map_dbl(sample, mean),
      se = map_dbl(sample, ~sd(.x)/sqrt(length(.x))),
      .lower = qTF(0.025, mean, se, nu = nu),
      .upper = qTF(0.975, mean, se, nu = nu)
    ) %>%
    ggplot() + 
    geom_pointinterval(aes(x = 0.5, y = mean), fill = "#333333", point_size = 5, interval_size = 12) +
    geom_point(aes(x = -0.5, y = pop_mean), color = "#C44232", size = 5) +
    geom_hline( yintercept = 0, size = 1, color = "red", alpha = 0.5 ) +
    scale_y_continuous( limits = limits, breaks = seq(limits[[1]], limits[[2]], by = 2) )  +
    scale_color_manual( values=c("#C44232", "#333333")) +
    theme(legend.position = "none") +
    ylab( "mean profit and 95% confidence interval" ) +
    xlim(-3, 3)

  ggsave(filename = paste0('../plots/example/profits-sol-t0-p0.5-', i, '.png'), height = 8, width = 5, units = "in", dpi = 72, type = "cairo-png", plot = p, device = "png")
}
```

```{r, fig.width = 10, fig.height = 4, eval = FALSE}
for(i in 1:n_regions) {
  p <- data.sample %>%
    filter(trial == 3 & region_idx == i) %>%
    rename(sample = profit, population = data) %>%
    mutate( 
      mean = map_dbl(sample, mean),
      se = map_dbl(sample, ~sd(.x)/sqrt(length(.x))),
      .lower = qTF(0.025, mean, se, nu = nu),
      .upper = qTF(0.975, mean, se, nu = nu)
    ) %>%
    ggplot(aes(x = NA, y = mean), fill = "#333333") + 
    geom_pointinterval(position = position_dodge(width = 0.2), size = 16) +
    geom_hline( yintercept = 0, size = 1, color = "red", alpha = 0.5 ) +
    scale_y_continuous( limits = limits, breaks = seq(limits[[1]], limits[[2]], by = 2) )  +
    theme(legend.position = "none") +
    ylab( "mean profit and 95% confidence interval" )

  ggsave(filename = paste0('../plots/example/profits-t0-p0.5-', i, '.png'), height = 8, width = 5, units = "in", dpi = 72, type = "cairo-png", plot = p, device = "png")
}
```


```{r, plot-mean-ci, fig.width = 10, fig.height = 4, eval = FALSE}
for(i in 1:n_regions) {
  for(j in 1:(n_trials * length(effect_sizes) * length(means))) {
    p <- data.sample %>%
      filter( trial == j & region_idx == i ) %>%
      mutate( 
        mean = map_dbl(profit, mean),
        se = map_dbl(profit, ~sd(.x)/sqrt(length(.x))),
        .lower = qTF(0.025, mean, se, nu = nu),
        .upper = qTF(0.975, mean, se, nu = nu)
      ) %>%
      ggplot(aes(x = NA, y = mean)) + 
      geom_pointinterval(point_size = 5, interval_size = 12) +
      geom_hline( yintercept = 0, size = 1, color = "red", alpha = 0.5 ) +
      scale_y_continuous( limits = limits, breaks = seq(limits[[1]], limits[[2]], by = 2) ) +
      ylab( "mean profit and 95% confidence interval" )
    
    ggsave(filename = paste0('../plots/ci/profits-t', j, '-p0.5-', i, '.png'), height = 8, width = 5, units = "in", dpi = 72, type = "cairo-png", plot = p, device = "png")
  }
}
```


### 5. Gradient plots

```{r, fig.width = 10, fig.height = 4}
data.sim.boot %>%
  filter(trial == 2 & region_idx == 3) %>%
  unnest( cols = c(boot.mean) ) %>%
  group_by(region) %>%
  ggplot(aes(y = boot.mean, x = NA)) +
  stat_gradientinterval(fill = "blue", show_interval = TRUE) +
  scale_alpha_continuous(range = c(0, 1)) +
  facet_wrap( ~ region_idx, ncol = 5 ) +
  labs( alpha = "density" ) +
  geom_hline( yintercept = 0, alpha = 0.5, color = "red" ) +
  ylim( limits )
```


### 6. Hypothetical outcome plots

```{r, hops, fig.width = 10, fig.height = 4}
n_samples = 50

data.sim.boot %>%
  filter(trial == 1 & p_h1 == 0.5) %>%
  unnest( cols = c(boot.mean) ) %>%
  group_by(region) %>%
  sample_n( n_samples ) %>%
  mutate( mean.index = 1:n_samples) %>%
  ggplot(aes(x = NA, y = boot.mean)) +
  geom_point() +
  facet_wrap( ~ region, ncol = 5 )  +
  geom_hline( yintercept = 0, alpha = 0.5, color = "red" ) +
  gganimate::transition_manual( mean.index )
```



### 7. Probability Density Function

```{r, plot-mean-density, fig.width = 3.5, fig.height = 6}
data.sim.boot  %>%
  filter(trial == 2 & region_idx == 3) %>%
  unnest( cols = c(boot.mean) ) %>%
  ggplot( aes(x = NA, y = boot.mean) ) +
  stat_halfeye(point_size = 5, interval_size = 8) +
  facet_wrap( ~ region, ncol = 5 ) +
  geom_hline( yintercept = 0, alpha = 0.5, color = "red" ) +
  scale_y_continuous( limits = limits, breaks = seq(limits[[1]], limits[[2]], by = 2) )  +
  ylab( "probability distribution of mean profit" )
```

```{r, pred-density, fig.width = 10, fig.height = 4, eval = FALSE}
for(i in 1:n_regions) {
  for(j in 1:(n_trials * length(effect_sizes) * length(means))) {
    p <- data.sim.boot %>%
      filter( trial == j & region_idx == i ) %>%
      unnest( cols = c(boot.mean) ) %>%
      ggplot( aes(x = NA, y = boot.mean) ) +
      stat_halfeye(point_size = 5, interval_size = 8) +
      geom_hline( yintercept = 0, size = 1, alpha = 0.5, color = "red" ) +
      scale_y_continuous( limits = limits, breaks = seq(limits[[1]], limits[[2]], by = 2) )  +
      ylab( "probability distribution of mean profit" )

    ggsave(filename = paste0('../plots/halfeye/profits-t', j, '-p0.5-', i, '.png'), height = 8, width = 5, units = "in", dpi = 72, type = "cairo-png", plot = p, device = "png")
  }
}
```


### 8. Quantile dot plots

```{r, plot-mean-density, fig.width = 10, fig.height = 4}
p <- data.sim.boot  %>%
  filter(trial == 2 & region_idx == 3) %>%
  unnest( cols = c(boot.mean) ) %>%
  ggplot( aes(x = NA, y = boot.mean) )  +
  stat_dots(position = "dodge", quantiles = 50) +
  facet_wrap( ~ region, ncol = 5 ) +
  geom_hline( yintercept = 0, alpha = 0.5, color = "red" ) +
  coord_cartesian( ylim = c(-2, 4))

pdf(file = "../figures/dots.pdf", useDingbats = FALSE, width = 5, height = 8)
p
dev.off()
```
